\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Tailwaggr: A One-Stop Shop for All Things Pet}
\author{Argonauts}

\begin{document}

\maketitle

\section{Introduction}

Tailwaggr's vision is to be a one-stop shop for all things pet, fostering a vibrant and supportive online community for pet owners and enthusiasts.

Our objectives are to:

\begin{itemize}
\item Empower pet owners: Provide a platform that simplifies pet care and strengthens the bond between owners and their furry companions.
\item Connect the pet care community: Facilitate connections between pet owners, veterinarians, pet sitters, and other animal lovers through forums and relevant services.
\item Enhance pet well-being: Offer resources and tools that promote responsible pet ownership and contribute to the overall health and happiness of pets.
\end{itemize}

\section{Business Need}

The pet care industry is booming, with a growing number of people considering pets as valued members of their families.  Tailwaggr addresses this need by:

\begin{itemize}
\item Centralizing pet care resources: Simplifying the process of finding qualified pet care professionals and relevant pet information.
\item Enhancing convenience: Offering a mobile app allows pet owners to manage their pet's needs and access services on the go.
\item Building a community: Providing a platform for pet owners to connect, share experiences, and offer support to each other.
\end{itemize}

\section{Project Scope}

The initial scope of Tailwaggr focuses on core functionalities:

\begin{itemize}
\item Pet profiles and owner profiles: Create detailed profiles for pets and their owners, fostering a sense of community and personalization.
\item Find a veterinarian: Allow pet owners to locate and connect with licensed veterinarians in their area.
\item Find a pet sitter: Enable pet owners to discover reliable pet sitters and dog walkers for in-home or scheduled pet care.
\item Pet forums: Establish a dedicated forum section where pet owners can ask questions, share experiences, and build relationships.
\item Lost \& Found Pets: Create a database to reunite lost pets with their worried owners and facilitate faster reunions.
\end{itemize}

Future iterations may consider expanding the scope to include features like:

\begin{itemize}
\item Appointment scheduling with veterinarians and pet sitters.
\item Telehealth consultations with veterinarians.
\item Online pet stores or marketplaces.
\item Integration with wearable pet trackers.
\end{itemize}

\section{User Characteristics and Stories}

\section{Functional Requirements}

\section{Use Case Diagrams}

\section{Quality Requirements}

\end{document}
